Local simple connectedness of boundaries of hyperbolic groups

### 2020-03-11 paper.tex
Modified the definition of the H_i
This makes some later things work better, and I don't think it breaks
anything.

\section{Horoballs in the Rips Complex}\label{sec:horoballs}

@@

For each $n$, let $v_n$ be a vertex of $K_n$ and let $g_n$ be an element of $G$
taken so that $g_n\cdot v_n$ is a point $v \in K_n$ independent of $n$.  Since
$K$ is locally finite, we can pass to a subsequence so that $v_i \in
K_{n_i}$ satisfies the following conditions:
\begin{enumerate}
  \item
    The translates by $g_i$ of large neighbourhoods of $v_i$ in the sphere
    $S_{n_i} \subset G$ are equal: for any $i \geq j$,
    \begin{equation*}
      g_i\left(N_j(v_i) \intersection S_{n_i}\right) 
            = g_j\left(N_j(v_j) \intersection S_{n_j}\right).
    \end{equation*}
    (Here $N$ denotes a neighbourhood taken with respect to the word metric on
    $G$.)
  \item
    The sequence $g_i = g_i\cdot 1$ of vertices of $K$ converges to a point
    $\xi \in \boundary G$ as $i\to\infty$.
\end{enumerate}

Let $H_i$ be the full subcomplex of $K$ with vertex set
\begin{equation*}
  g_i\left(N_i(v_i) \intersection S_{n_i}\right);
\end{equation*}
notice that $H_i$ contains $H_j$ for $i \geq j$, and also that $g_i$ maps the
full subcomplex of $K_{n_i}$ with vertex set $N_i(v_i) \intersection S_{n_i}$
isometrically onto $H_i$.

Let $H$ be the union of the complexes $H_i \subset K$. We view $H$ as a
horosphere, the topology of which approximates that of $\boundary G - \set\xi$.
The rest Section of~\ref{sec:horoballs} will be spent justifying this point of view.

@@

\begin{proof}
  \todo{Check the claim about neighbourhoods being equal.}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$, and so does not meet $H_i\intersection
  N_{i-4\delta-1}(v)$, which is equal to $H \intersection N_{i-4\delta-1}(v)$.
  After passing to a subsequence, the rays $\alpha_i$ converge uniformly on
  compact subsets to a bi-infinite geodesic from $\xi$ to some point $\zeta \in
  C$ that does not meet $H$, contradicting
  Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}

>>>>

\section{Horoballs in the Rips Complex}\label{sec:horoball}

@@

For each $n$, let $v_n$ be a vertex of $K_n$ and let $g_n$ be an element of $G$
taken so that $g_n\cdot v_n$ is a point $v \in K_n$ independent of $n$.  Since
$K$ is locally finite, we can pass to a subsequence so that $v_i \in
K_{n_i}$ satisfies the following conditions:
\begin{enumerate}
  \item
    The translates by $g_i$ of large neighbourhoods of $v_i$ in the sphere
    $S_{n_i} \subset G$ are equal: for any $i \geq j$,
    \begin{equation*}
      N_j(v) \intersection g_i(S_{n_i}) = N_j(v) \intersection g_j(S_{n_j})
    \end{equation*}
    (Here $N$ denotes a neighbourhood taken with respect to the word metric on
    $G$.)
  \item
    The sequence $g_i = g_i\cdot 1$ of vertices of $K$ converges to a point
    $\xi \in \boundary G$ as $i\to\infty$.
\end{enumerate}

Let $H_i$ be the full subcomplex of $K$ with vertex set $N_i(v) \intersection
g_i(S_{n_i})$; notice that $H_i$ contains $H_j$ for $i \geq j$, and also that
$g_i$ maps the full subcomplex of $K_{n_i}$ with vertex set $N_i(v_i)
\intersection S_{n_i}$ isometrically onto $H_i$.

Let $H$ be the union of the complexes $H_i \subset K$. We view $H$ as a
horosphere, the topology of which approximates that of $\boundary G - \set\xi$.
The rest Section of~\ref{sec:horoball} will be spent justifying this point of view.

@@

\begin{proof}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$, and so does not meet $H_i\intersection
  N_{i-4\delta-1}(v)$, which is equal to $H \intersection N_{i-4\delta-1}(v)$.
  After passing to a subsequence, the rays $\alpha_i$ converge uniformly on
  compact subsets to a bi-infinite geodesic from $\xi$ to some point $\zeta \in
  C$ that does not meet $H$, contradicting
  Lemma~\ref{lem:geodesicsmeethorosphere}.
\end{proof}
